Untitled

### 2017-07-14 PaperCode.Rmd
Fix plotmap
Fixed a bug in plot map which stopped it from plotting other variables.

@@

#Hull
```{r}

HullDATA <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
  StructureData(.)

@@

#number of LUPS and Total Homes
ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  summarise(
           TotalLads = length(unique(LAD11CD)),
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           Poperc = Population/sum(EW2$Pop))

@@

@@

#MakeLeaflet(SouthwarkLONDATA)

@@

@@

test <- BootStrapRES$CoastWave
#look at specific data
BootStrapRES$SouthwarkLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

>>>>

Should type B be included? or just type A?

@@

#Yorkshire and the Humber
```{r}
setwd(file.path(RegionsComp, "Region Yorkshire and The Humber"))

#Hull

HullDATA <-read_excel("KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX")[-c(c(1:6)),1:4] %>%
  StructureData(.)

#Harrowgate

HarrogateDATA <-read_excel("Harrogate DiscountsExemptionsLSOA.xlsx" )[,1:4] %>%
  StructureData(.,3:10)

#Wales

setwd(file.path(RegionsComp, "Region Wales"))
list.files()

CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse =c(8:13,15))

@@

#number of LUPS and Total Homes
ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  filter(!is.na(LAD11NM)) %>%
  summarise(
           TotalLads = length(unique(LAD11CD)),
           LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T),
           PercHomes = Homes/sum(EW2$Homes),
           Population = sum(Pop, na.rm= T),
           Poperc = Population/sum(EW2$Pop))

@@

#check which lads are present even though I don't have data due to postcode matching
#test <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x)))  %>% arrange(LAD11NM)
#unique(test$LAD11NM)

@@

z<- MakeLeaflet(CeredigionDATA)
z

saveWidget(z, file=file.path(basewd, "CeredigionDATA"), selfcontained = TRUE )

@@

#Investigating Ceredigion

CeredPrice <- prices %>% 
  filter( grepl("W06000008", Admin_district_code)) %>%
  select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
  #filter(X15 == "A") %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                     right = F),
         Price = as.numeric(Price))

CeredPrice2 <- CeredPrice %>%
  group_by(lsoa11cd, class) %>%
  summarise(Admin_ward_code = first(Admin_ward_code),
            LSOAcounts = n())

CeredPrice2 <- CeredPrice2  %>%
  group_by(Admin_ward_code, class) %>%
  summarise(counts = n()) %>%
  group_by(class) %>%
  mutate(ClassPercent = counts/sum(counts)) %>%
  ungroup %>% group_by(Admin_ward_code) %>%
  mutate(WardPercent = counts/sum(counts))%>%
  left_join(CeredPrice2,. ,by=c("Admin_ward_code", "class")) %>%
  rename(LSOA_CODE = lsoa11cd)

RBKCPrice <- prices %>% 
  filter( grepl("E09000020", Admin_district_code)) %>%
    select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
  #filter(X15 == "A") %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                     right = F),
         Price = as.numeric(Price))

RBKCPrice2 <- RBKCPrice %>%
  group_by(lsoa11cd, class) %>%
  summarise(Admin_ward_code = first(Admin_ward_code),
            LSOAcounts = n())

RBKCPrice2 <- RBKCPrice  %>%
  group_by(Admin_ward_code, class) %>%
  summarise(counts = n()) %>%
  group_by(class) %>%
  mutate(ClassPercent = counts/sum(counts)) %>%
  ungroup %>% group_by(Admin_ward_code) %>%
  mutate(WardPercent = counts/sum(counts))%>%
  left_join(RBKCPrice2,. ,by=c("Admin_ward_code", "class")) %>%
  rename(LSOA_CODE = lsoa11cd)

RBKCtot <- RBKCPrice2 %>%
  group_by(class) %>%
  summarise(counts = sum(counts))

summary(CeredPrice$Price)
summary(RBKCPrice$Price)

RBKCPrice %>% group_by(X15) %>%
  summarise(mean = mean(Price))

CeredPrice %>% group_by(X15) %>%
  summarise(mean = mean(Price))

 RBKCPrice2 %>%
   filter(class == "Prime") %>%
   PlotMap(.,AG,  "ClassPercent")

  CeredPrice2 %>%
   filter(class == "Mid") %>%
   PlotMap(.,filter(AG, LAD11CD=="W06000008"), variable = "ClassPercent", filtermap = FALSE)

@@

test <- BootStrapRES$Ceredigion
#look at specific data
BootStrapRES$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

prices %>%
